Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-04 submission.tex
Minor changes

\begin{table} \centering
    %\smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Head} & \textbf{Dependent} \\
        \midrule
        Preposition & Prepositional complement \\
        Finite verb & Complementizer \\
        First conjunct & Subsequent conjuncts \\
        Finite auxiliary & Lexical/main verb \\
        Noun & Determiner \\
        \bottomrule
    \end{tabular}
    \caption{Annotation choices in NDT.}
    \label{ndtannotation}
\end{table}

@@

\paragraph{Tagger}
For our experiments with tag set modifications, we wanted a PoS tagger both
reasonably fast and accurate. There is often a trade-off between the two
factors/considerations, as the most accurate taggers tend to suffer in terms of
speed due to their complexity. However, a tagger that achieves both close to
state-of-the-art accuracy as well as very high speed is TnT \cite{Bra:00}. The
fact that TnT was used for evaluating the universal tag set
\cite{Pet:Das:McD:12}, served as another good indication of TnT being
appropriate for our task. The sum of these factors led to TnT being the tagger
of choice for our experiments.

@@

\paragraph{Tags \& Features}
As we seek to quantify the effects of PoS tagging in a realistic setting, we
want to run the parser on automatically assigned PoS tags. For the training of
the parser, however, we have two options: using either gold standard or
automatically assigned tags. In order to settle on a configuration, we
conducted experiments with gold standard and automatically assigned tags to see
how they differ with respect to performance. The results of our experiments
reveal that the combination of training and testing on automatic tags is
superior to training on gold standard tags and testing on automatic tags.
Consequently, the parser was both trained and tested on automatically assigned
tags in our experiments.

>>>>

\begin{table} \centering
    %\smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Head} & \textbf{Dependent} \\
        \midrule
        Preposition & Prepositional complement \\
        Finite verb & Complementizer \\
        First conjunct & Subsequent conjuncts \\
        Finite auxiliary & Lexical/main verb \\
        Noun & Determiner \\
        \bottomrule
    \end{tabular}
    \caption{Central head-dependent annotation choices in NDT.}
    \label{ndtannotation}
\end{table}

@@

\paragraph{Tagger}
For our experiments with tag set modifications, we wanted a PoS tagger both
reasonably fast and accurate. There is often a trade-off between the two
factors/considerations, as the most accurate taggers tend to suffer in terms of
speed due to their complexity. However, a tagger that achieves both close to
state-of-the-art accuracy as well as very high speed is TnT \cite{Bra:00}. TnT was furthermore recently used to evaluate the recently proposed universal tag set
\cite{Pet:Das:McD:12}. The sum of these factors led to TnT being the tagger
of choice for our experiments.

@@

\paragraph{Tags \& Features}
As we seek to quantify the effects of PoS tagging in a realistic
setting, i.e. in application to raw text, we want to evaluate the parser on
automatically assigned PoS tags. For the training of the parser,
however, we have two options: using either gold standard or
automatically assigned tags. In order to settle on a configuration, we
conducted experiments with gold standard and automatically assigned
tags to see how they differ with respect to performance. The results
of our experiments reveal that the combination of training and testing
on automatic tags is superior to training on gold standard tags and
testing on automatic tags.  Consequently, the parser was both trained
and tested on automatically assigned tags in our experiments.
